A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-23 bioc-workflow.Rmd
added section on unsupervised ML

>>>>

## Unsupervised machine learning
In `pRoloc` there is functionality for unsupervsied machine learning
methods. In unsupervised learning, the training data consists of a
set of input vectors e.g. protein profiles, for which we do not have
information about the class label e.g. localisation. The main goal in
unsupervised learning is to uncover groups of similar examples within
the data, this is termed clustering. Ordinance methods such as
principal components analysis (PCA) also fall into the category of
unsupervised learning methods, where the data can be projected from a
high-dimensional spcae down to two or three dimensions for the purpose
of visualisation.

As described and demonstrated already above, PCA is a valuable and
powerful method for data visualisation and quality control. We do not
do any unsupervised clustering in the frame of the above spatial
proteomics workflow as although clustering can be useful for grouping
labelled data into categories e.g. see the `mrkHClust` function, we do
not find it adaquete for protein localisation prediction and spatial
proteomics data analysis in general.
